---
title: "Analyze lab values"
output: html_document
---


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(vroom)
library(lubridate)
```


```{r}
system.time(
  lab_values <- vroom('../Penn_ICU_Data/ICU PTS COHORT LABS.csv', delim = ',')
)
lab_values_first_mil <- slice(lab_values, 1:10^6)
# save(lab_values, file = '../Penn_ICU_Data/lab_values_small.Rdata')
# load('../Penn_ICU_Data/lab_values_small.Rdata')'
```



```{r}
table_10_e6 <- function(var, n = 50){
  lab_values %>% 
    select(!!enquo(var)) %>% 
    slice(1:10^6) %>% 
    table() %>% 
    sort(decreasing = T) %>%
    head(n)
}
table_10_e6(ORDER_NAME)
table_10_e6(RESULT_RESOURCE)
table_10_e6(RESULT_ITEM_CODE)
str(head(lab_values))
```


```{r}
keep_orders <- c('CBC w/ Auto Diff', 'Basic Metabolic Panel', 'CBC w/ Platelets', 
                 '_Automated Differential', 'Liver Injury Panel', 'PT', 'Magnesium Level', 
                 'Panel 5 (Na K CO2 Cre Un)', 'PT/APTT', 'PTT', 'ABSC', 'Phosphorus Level',
                 'Drug Screen, Urine', 'ABORh Type PAH', 'Chem11', 'Liver Evaluation Panel',
                 'Lactic Acid (CC Lab)', 'Hepatic Function Panel', 'UA PAH',
                 'Na & K (CC Lab)', 'Chem16 Component Of Nstpn')

lab_values_anal <- lab_values %>%
  filter(ORDER_NAME %in% keep_orders)
```


             CBC w/ Auto Diff         Basic Metabolic Panel              CBC w/ Platelets       _Automated Differential 
                       142918                        136250                        107456                         94870 
         ABL90 Arterial Panel                   Manual Diff   Glucose (Plasma Rals Group)            ABL90 Venous Panel 
                        85813                         56254                         35794                         21048 
               ABORh Type HUP     Blood Gas Arterial Vented           Urinalysis Dipstick            Liver Injury Panel 
                        20306                         18407                         17221                         16620 
                           PT                Newborn Screen Comprehensive Metabolic Panel               Magnesium Level 
                        14078                         11604                         11296                         10067 
    Panel 5 (Na K CO2 Cre Un)                       PT/APTT                           PTT        Urinalysis Microscopic 
                         9004                          8394                          7822                          7613 
                         ABSC              Phosphorus Level            Drug Screen, Urine                ABORh Type PAH 
                         7578                          6921                          6015                          6003 
              _ABG/Lytes Rals                       Ab Scrn Blood Gas Arterial Non-Vented                    ABORh PPMC 
                         5202                          4767                          4702                          4301 
                       AT-HUP               Patient History              Blood Gas Venous                RBC Morphology 
                         4032                          3901                          3646                          3513 
                       Chem11        Liver Evaluation Panel          Lactic Acid (CC Lab)     _ABG/Lytes Rals Capillary 
                         3284                          3262                          2951                          2858 
       Hepatic Function Panel                        UA PAH               Na & K (CC Lab)     Chem16 Component Of Nstpn 
                         2743                          2689                          2601                          2586 
                    _ABG Rals          Chem 8 Point of Care         WBC Corrected (Group)                           EXM 
                         2401                          1876                          1724                          1668 
              GEM4000 ANLCOOX       Hgb/O2 SATURATION (SCM)                Blood Gas Cord       GEM Premier Arterial BG 
                         1666                          1613                          1400                          1377 
       _ABG/Lytes Rals Venous              Cooximetry Panel 
                         1339                          1335 
                              

```{r}
grep('VBG', lab_values$ORDER_NAME[1:10^7], ignore.case = T)
system.time(grep('prbc', lab_values$ORDER_NAME, ignore.case = T))
system.time(ph_idx <- grep('pH', lab_values$ORDER_NAME))

```
No 'VBG' is found in ORDER_NAME.

RBC Morphology?
                              
```{r}
system.time(
  abgs <- lab_values[grep('ABG', lab_values$ORDER_NAME, ignore.case = T),]
)
head(abgs)
head(abgs$RESULT_DATE)
```



