---
title: "Analyze the complete datasets"
output: html_document
---
## Setup:

```{r}
library(tidyverse)
library(vroom)
library(lubridate)
```

## Utils

Load utility functions:

```{r}
source('utils.R')
```

## Read in data:

```{r}
data_path <- '../wharton/processed_data/' 
ori_data_path <- '../wharton/data/'

k_d <- read_d('k')
k_d_all <- read_ori('potassium_data')
hospital_d <- read_ori('visit_hospital')
k_all_visits <- k_d_all$visit_num %>%
  unique()

code_list <- read_csv('codenames.csv') %>%
  split(.$V1) %>%
  map(visits)
```

Note: `k_d` has 109723 observations/repletions but only 50470 unique visits.


### Add variables to vitals_d

Calculate GFR by MDRD calculation
female_coeff = 0.742 if is_female==1 else 1
aa_coeff = 1.212 if_aa==1 else 1
(assuming no African-American patients - data not available)
$GFR = 175 * Cr^{-1.154} * age^{-0.203} * femalefactor$


```{r}
daily_dat <- c('daily_vitals', 
               paste0('given_', c('fluid_bolus', 'beta_blocker', 'diltiazem', 'amiodarone')), 
               'creatinine', 'is_ventilated', 
               paste0(c('potassium', 'magnesium', 'calcium', 'phosphate'), '_daily_labs'))

system.time(
  vitals_d <- lapply(daily_dat, read_ori) %>%
    reduce(left_join, by = c('visit_num', 'day_in_unit')) %>%
    list() %>%
    c(lapply(c('age_gender', 'weights', 'visit_hospital'), read_ori)) %>%
    reduce(left_join, by = 'visit_num') %>%
    mutate(gfr_mdrd = 175 *
             creatinine^(-1.154) *
             age^(-0.203) *
             ifelse(is_female, 0.742, 1)) 
)

gfr_info <- vitals_d %>%
  filter((gfr_mdrd > 0) & (gfr_mdrd < 30)) %>%
  select(visit_num) %>%
  unique() %>%
  mutate(gfr_mdrd_below_30 = TRUE) %>%
  add_F('gfr_mdrd_below_30')

```


### Add variables to `k_d`:

```{r}
system.time(
  k_ext <- k_d_all %>%
    mutate(delta_val = post_repletion_val - pre_repletion_val,
           performed_day_of_week = performed_date %>% ymd_hms() %>% weekdays(),
           performed_date_only = performed_date %>% ymd_hms() %>% date() %>% as.character(),
           performed_dose = performed_dose * ifelse(
             (is_iv == 1) & grepl('phosphate', medication_name, ignore.case = T),
             4.4/3.0,
             1) # adjust for 4.4 mEq K / 3 mmol P in KH2PO4 only K dataframe!
    ) %>%
    group_by(visit_num, 
             pre_repletion_val_date_offset_seconds,
             post_repletion_val_date_offset_seconds) %>%
    add_tally() %>%
    mutate(is_ivpo = as.integer(skimr::n_unique(is_iv) > 1)) %>%
    ungroup() %>%
    list() %>% 
    c(code_list, list(gfr_info, hospital_d)) %>%
    reduce(left_join, by = 'visit_num')
)

# Checking columns:
setdiff(colnames(k_d), colnames(k_ext))
# setdiff(colnames(dv_d), colnames(vitals_d))
identical(k_d$gfr_mdrd_below_30_x, k_d$gfr_mdrd_below_30_y)
# It's a match! `group_size` is `n`.
```




Note: quite a few missing "age".

Now let's filter:

```{r}
vitals_merged <- vitals_d %>%
  merge(k_ext,
        by.x = c('visit_num', 'day_in_unit'),
        by.y = c('visit_num', 'performed_date_only')
  )
# table(vitals_merged$prbc_given)
visits_to_exclude <- vitals_merged %>%
  filter(on_tpn |               # on TPN
           is_rhabdo |          # rhabdomyolysis code
           is_parathyroid |     # parathyroid disorders of any kind
           is_sarcoid |         # sarcoid disorders of any kind
           is_esrd |            # code for ESRD
           is_dialysis |        # code for dialysis
           given_dialysis |     # dialysis procedure
           age < 18 |
           # prbc_given == 1 |
           gfr_mdrd < 30
  ) %>%
  pull(visit_num) %>%
  unique()

table(vitals_d$prbc_given)
```


```{r}
visit_num_filtered <- vitals_d %>%
  # filter(
  #   (age >= 18) & # over 18 years old
  #     prbc_given == 0 # no PRBC
  # ) %>%
  # filter(is.na(gfr_mdrd) | gfr_mdrd > 30) %>%
  pull(visit_num) %>%
  unique() %>%
  setdiff(visits_to_exclude)

# Include patients:
k_filtered <- k_ext %>%
  filter((visit_num %in% visit_num_filtered)   # no dialysis procedure
  ) %>%
  filter(pre_repletion_val >= 2.0 & 
           pre_repletion_val <= 7.0 & 
           delta_val <= 4.0 &
           n <= 1
  )
vitals_filtered <- vitals_merged %>%
  filter((visit_num %in% visit_num_filtered)   # no dialysis procedure
  ) %>%
  filter(pre_repletion_val >= 2.0 & 
           pre_repletion_val <= 7.0 & 
           delta_val <= 4.0 &
           n <= 1
  )
k_ext %>% filter(gfr_mdrd_below_30) %>% nrow()
k_filtered %>% pull(visit_num) %>% unique() %>% length()
save(vitals_filtered, file = 'vitals_filtered_prbc.Rdata')
```

From jpynb:
K repletions in k_d: 430137
Mg repletions in mg_d: 238410
Ca repletions in ca_d: 15740
Phos repletions in phos_d: 49979
ICU days in dv_d: 9786414

Will exclude 50926 visits: patients were under 18 years old
```{r}
vitals_d %>% filter(age < 18 | is.na(age)) %>% pull(visit_num) %>% unique() %>% length()
```

Will exclude 39116 visits: patients got PRBCs
```{r}
vitals_d %>% filter(prbc_given == 1) %>% pull(visit_num) %>% unique() %>% length()
```

Will exclude 9138 visits: patients had TPN orders of some kind
```{r}
vitals_merged %>% filter(!on_tpn) %>% pull(visit_num) %>% unique() %>% length() # 8234
```

Will exclude 853 visits: patients had rhabdomyolysis codes
```{r}
k_ext %>% filter(is_rhabdo) %>% pull(visit_num) %>% unique() %>% length() # 720
```

Will exclude 642 visits: patients had parathyroid disorders of any kind
```{r}
k_ext %>% filter(is_parathyroid) %>% pull(visit_num) %>% unique() %>% length() # 463
```

Will exclude 1073 visits: patients had sarcoid disorders of any kind
```{r}
k_ext %>% filter(is_sarcoid) %>% pull(visit_num) %>% unique() %>% length() # 883
```

Will exclude 3702 visits: patients had codes for ESRD, dialysis, or both
```{r}
k_ext %>% filter(is_esrd|is_dialysis) %>% pull(visit_num) %>% unique() %>% length() # 2141
# k_ext %>% filter(is_dialysis) %>% pull(visit_num) %>% unique() %>% length()
```

Will exclude 4058 visits: patients had some kind of dialysis procedure
```{r}
k_ext %>% filter(given_dialysis) %>% pull(visit_num) %>% unique() %>% length() # 2589
# vitals_d %>% filter(given_dialysis) %>% pull(visit_num) %>% unique() %>% length() # 2589

```

Will exclude 41829 visits: patients had a recorded GFR under 30 at any point
   (though patients with no GFR values were left in)
```{r}
vitals_merged %>% filter(gfr_mdrd_below_30) %>% pull(visit_num) %>% unique() %>% length() # 13675
# k_ext %>% filter(!gfr_mdrd_below_30) %>% pull(visit_num) %>% unique() %>% length()
# vitals_d %>%
#   filter((gfr_mdrd > 0) & (gfr_mdrd < 30)) %>% pull(visit_num) %>% unique() %>% length()
# vitals_d %>% filter(gfr_mdrd_below_30) %>% pull(visit_num) %>% unique() %>% length()

k_ext %>% filter(n<=1) %>% nrow() # 260796
```


```{r}
visits_kd <- k_d %>% pull(visit_num) %>% unique()
visits_kfiltered <- k_filtered %>% pull(visit_num) %>% unique()
```



Note all these exclusions are from the original set, NOT stepwise, so a given patient may be excluded for more than one reason

After those exclusions:
K repletions in k_d: 182413
Mg repletions in mg_d: 98246
Ca repletions in ca_d: 2898
Phos repletions in phos_d: 16902
ICU days in dv_d: 3128249
Number of visits in dv_d: 332018


