---
title: "Preliminary analyses"
output: html_document
---
## Setup:

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(vroom)
library(lubridate)
```

## Utils

Load utility functions:

```{r}
source('utils.R')
```

## Read in data:

```{r}
data_path <- '../wharton/processed_data/' 
ori_data_path <- '../wharton/data/'

load('vitals_filtered_prbc.Rdata')
k_d <- read_d('k')
mg_d <- read_d('mg')
ca_d <- read_d('ca')
phos_d <- read_d('phos')
dv_d <- read_d('dv')
k_d_all <- read_ori('potassium_data')
hospital_d <- read_ori('visit_hospital')
k_all_visits <- k_d_all$visit_num %>%
  unique()
```

```{r}
# extend k_d dataset
k_d <- k_d %>%
  mutate(t_order = order_date_offset_seconds - pre_repletion_val_date_offset_seconds,
         t_RN = performed_date_offset_seconds - pre_repletion_val_date_offset_seconds,
         t_orderlab = post_repletion_val_order_date_offset_seconds - pre_repletion_val_date_offset_seconds,
         t_resultlab = post_repletion_val_date_offset_seconds - post_repletion_val_order_date_offset_seconds,
         t_repletion_orderlab_overlap = post_repletion_val_order_date_offset_seconds - performed_date_offset_seconds,
         t_repletion_resultlab_overlap = post_repletion_val_date_offset_seconds - performed_date_offset_seconds,
         weekend = performed_day_of_week >= 5)
```

## PRBC
How much are potassium level changes depending on the transfusion of PRBC?

```{r}
lm(delta_val ~ performed_dose + pre_repletion_val + is_cad + is_chf + is_ckd + on_loop_diuretic + on_acetazolamide + on_thiazide + on_spironolactone + prbc_given, data = vitals_filtered) %>%
  summary() %>%
  broom::tidy() %>%
  mutate(padj = p.adjust(p.value, method = 'BH'))

# What about other variables?

lm(delta_val ~ performed_dose + pre_repletion_val + is_cad + is_chf + is_ckd + 
     on_loop_diuretic + on_acetazolamide + on_thiazide + on_spironolactone + 
     prbc_given + on_tpn + is_rhabdo + is_dialysis + given_dialysis + age, 
   data = vitals_filtered) %>%
  summary() %>%
  broom::tidy() %>%
  mutate(padj = p.adjust(p.value, method = 'BH'))



# lm(delta_val ~ performed_dose + is_cad + is_chf + is_ckd + on_loop_diuretic + on_acetazolamide + on_thiazide + on_spironolactone, data = k_d) %>%
#   summary() %>%
#   broom::tidy() %>%
#   mutate(padj = p.adjust(p.value, method = 'BH'))
# 
# lm(order_to_repletion_seconds ~ pre_repletion_val + is_cad + is_chf + is_ckd + on_loop_diuretic + on_acetazolamide + on_thiazide + on_spironolactone , data = vitals_filtered) %>%
#   summary() %>%
#   broom::tidy()
```

## Focus on pre-repletion value > 4.5

Descriptive stats:

```{r echo = F}
improper_k_d <- k_d %>% filter(pre_repletion_val > 4.5) 
improper_mg_d <- mg_d %>% filter(pre_repletion_val > 2.5)

k_d %>%
  count(provider_name) %>%
  nrow() %>%
  paste('Total number providers:', .) %>%
  print()

nrow(improper_k_d) %>%
  paste('total improper K repletions.') %>%
  print()

improper_k_d %>%
  count(provider_name) %>%
  nrow() %>%
  paste('providers perform improper K repletion.') %>%
  print()

improper_k_d %>%
  count(provider_name) %>%
  filter(n >= 10) %>%
  nrow() %>%
  paste('providers do it at least 10 times.') %>%
  print()

nrow(improper_mg_d) %>%
  paste('total improper Mg repletions.') %>%
  print() # 187

improper_mg_d %>%
  count(provider_name) %>%
  nrow() %>%
  paste('providers perform improper Mg repletion.') %>%
  print()

improper_mg_d %>%
  count(provider_name) %>%
  filter(n >= 5) %>%
  nrow() %>%
  paste('providers do it at least 5 times.') %>%
  print()

intersect(improper_mg_d$provider_name,
          improper_k_d$provider_name) %>%
  length() %>%
  paste('of these providers also improperly prescribe K.') %>%
  print()

table(vitals_filtered$prbc_given)
```


Hospitals: improper repletions and total repletions:

```{r}
improper_k_d %>%
  dplyr::select(provider_name, hospital) %>%
  count(hospital) %>%
  left_join(count(k_d, hospital), by = 'hospital') %>%
  mutate(frac = n.x/n.y)
```

What may affect a provider's decision to prescribe an improper repletion:

```{r}
k_d <- k_d %>% 
  mutate(improper_repletion = pre_repletion_val > 4.5) 

lm(improper_repletion ~ is_iv + gfr_mdrd_below_30_x + performed_day_of_week + hospital +
     on_tpn + is_aki + is_ckd + is_esrd + is_dialysis + is_sarcoid + is_afib + is_paralyzed + 
     is_rhabdo + is_parathyroid + 
     is_cad + is_chf + is_ckd + on_loop_diuretic + on_acetazolamide + on_thiazide + on_spironolactone,
   data = k_d) %>%
  summary() %>%
  broom::tidy()
# table(k_d$improper_repletion)
table(k_d$is_iv, k_d$improper_repletion)
table(k_d$is_ckd, k_d$improper_repletion)
table(k_d$is_afib, k_d$improper_repletion)
table(k_d$on_loop_diuretic, k_d$improper_repletion)
table(k_d$is_chf, k_d$improper_repletion)
table(k_d$on_thiazide, k_d$improper_repletion)
```


## Reproduce some plots:

### At what point do providers replete electrolytes?
Cell 15:

```{r}
k_d %>% group_by(provider_name) %>%
  add_tally(pre_repletion_val) %>%
  filter(n > 20) %>%
  summarise(mean_pre_rep_val = mean(pre_repletion_val)) %>%
  ggplot(aes(x = mean_pre_rep_val)) +
  geom_histogram(binwidth = 0.1) +
  labs(y = 'Number of providers')


# mydat <- k_d %>% group_by(provider_name) %>%
#   summarise(mean_pre_rep_val = mean(pre_repletion_val))
# hist(mydat$mean_pre_rep_val)
# ggplot(mydat, aes(x = mean_pre_rep_val)) +
#   geom_histogram(binwidth = 0.5)
```

Cell 17:

```{r}
boxplot(k_d$result_to_order_seconds)
# ymd_hms(k_d$performed_date) - ymd(k_d$result_to_order_seconds)
```



Cell 21:

```{r}
days <- c('Mon', 'Tue', 'Wed', 'Thu', 'Fri', 'Sat', 'Sun')
k_d %>%
  group_by(performed_day_of_week) %>%
  summarise(mean_pre_val = mean(pre_repletion_val)) %>%
  ggplot(aes(x = performed_day_of_week,
             y = mean_pre_val)) +
  geom_point() +
  scale_y_continuous(limits = c(0, 3.7))
```


### What are the pre- and post-repletion electrolyte lab values?
```{r}
k_d %>%
  dplyr::select(pre_repletion_val, post_repletion_val) %>%
  gather('prepost', 'value') %>%
  ggplot(aes(x = value, fill = prepost)) +
  geom_histogram(alpha = 0.7, position = 'identity', binwidth = 0.1)
```


```{r}
ineffective_proportion <- function(lyte){
  sum(lyte$delta_val < 0)/length(lyte$delta_val) # 20% for K
}

delta_repletion <- k_d$delta_val
sum(delta_repletion < 0)/length(delta_repletion) # 23%
ineffective_proportion(mg_d) # 20%
sum(phos_d$delta_val < 0)/length(phos_d$delta_val) # 16%
sum(ca_d$delta_val < 0)/length(ca_d$delta_val) # 20%

cor.test(delta_repletion, k_d$on_acetazolamide)
# t.test(alternative = 'greater')

```

last 6 hours dialysis, +/- 12 hours
excluded dialysis
why?
same patient: K drop, K increase?
heart rate: heart beat high
drug datasets






```{r}
lm(delta_val ~ performed_dose + 
     pre_repletion_val +
     is_cad + is_chf + is_ckd + on_loop_diuretic + on_acetazolamide + on_thiazide + on_spironolactone, data = k_d) %>%
  summary() %>%
  broom::tidy() %>%
  mutate(padj = p.adjust(p.value, method = 'BH'))

lm(delta_val ~ performed_dose + is_cad + is_chf + is_ckd + on_loop_diuretic + on_acetazolamide + on_thiazide + on_spironolactone, data = k_d) %>%
  summary() %>%
  broom::tidy()

cor(k_d$performed_dose, k_d$delta_val)

```

```{r}


ggplot(aes(x = t_order/60, fill = weekend), data = k_d) +
  geom_histogram(bins = 300, stat = 'density',
                 position = 'identity', alpha = 0.8) +
  scale_x_continuous(limits = c(-20000/60, 86400/60))
  labs(x = 'Time since initial lab resulted, in minutes',
       y = 'Proportion of occurrences')
```




```{r}
ggplot(aes(x = t_order/60, fill = weekend), data = improper_k_d) +
  geom_histogram(bins = 300, stat = 'density',
                 position = 'identity', alpha = 0.8) +
  scale_x_continuous(limits = c(-20000/60, 86400/60))
  labs(x = 'Time since initial lab resulted, in minutes',
       y = 'Proportion of occurrences')

# of the 2303 improper repletions, how many are before lab results come
improper_k_d %>%
  filter(t_order < 0) %>%
  filter(t_order > -20000) %>%
  nrow()
#181

k_d %>%
  filter(t_order < 0) %>%
  filter(t_order > -20000) %>%
  nrow()
#5947
```


Drugs to consider:
- Furosemide
- Lasix
- Spironolactone
- Diamox
- HCTZ
- Hydrochlorothiazide
- bumex

```{r}
# meds_d <- data.table::fread('../../Penn_ICU_Data/ICU PTS COHORT MEDS.csv')
# save(meds_d, file = '../wharton/data/medications.Rdata')

# load('../wharton/data/medications.Rdata')
# colnames(meds_d)
# head(meds_d)
# table(meds_d$MEDICATION_NAME[1:1000])
```

```{r}
# slice_drugs <- function(drug_name){
#   meds_d %>%
#     filter(grepl(drug_name, MEDICATION_NAME, ignore.case = T))
# }
# diamox <- slice_drugs("diamox|acetazolamide")
# bumex <- slice_drugs("bumex|bumetanide")
# hctz <- slice_drugs("microzide|hydrochlorothiazide|HCTZ")
# spironolactone <- slice_drugs("spironolactone|caroSpir|aldactone")
# lasix <- slice_drugs("lasix|furosemide")
# save(diamox, bumex, hctz, spironolactone, lasix,
#      file = '../wharton/data/blood_pressure_meds.Rdata')
# 
load('../wharton/data/blood_pressure_meds.Rdata')
```

```{r}
# head(diamox)
# diamox <- diamox %>%
#   mutate(diamox_date = mdy_hms(
#     PERFORMED_DATE, 
#     format = '%m/%d/%Y %H.%M.%S %p')
#     [-(nrow(diamox) +1)])
# head(k_d)
```


```{r}
# k_d_time <- k_d %>%
#   mutate(k_date = ymd_hms(
#     performed_date, 
#     format = '%Y-%m-%d %H:%M:%S')
#     [-(nrow(k_d) +1)])
# 
# 
# head(ymd_hms(k_d$performed_date, 
#     format = '%Y-%m-%d %H:%M:%S'))
# 
# colnames(k_d)
# # k_d$post_hr_max
# 
# 
# head(k_d$performed_date)
# head(diamox$PERFORMED_DATE)
# head(as.Date(diamox$PERFORMED_DATE, format = '%m/%d/%Y %H.%M.%S %p'))
# library(lubridate)
# date_test <- mdy_hms(diamox$PERFORMED_DATE, format = '%m/%d/%Y %H.%M.%S %p')
# length(diamox$PERFORMED_DATE)
# length(date_test)
# tail(date_test)
# tail(diamox$PERFORMED_DATE, 5)
# diamox$PERFORMED_DATE[which(is.na(date_test))]
# dhours(date_test[1] - date_test[2])
# 
# date_test[1] %within% 
#   interval(date_test[1] - hours(12), date_test[1] + hours(12))
```



```{r}
vitals_filtered %>%
  # mutate(on_acetazolamide = as.factor(on_acetazolamide)) %>%
  ggplot(aes(x = prbc_given, y = delta_val, group = as.factor(prbc_given))) +
  geom_boxplot(aes(fill = as.factor(prbc_given))) +
  scale_fill_brewer(palette = 'Dark2')

# k_d %>%
#   mutate(on_acetazolamide = as.factor(on_acetazolamide)) %>%
#   ggplot(aes(x = on_acetazolamide, y = delta_val)) +
#   geom_boxplot(aes(fill = on_acetazolamide)) +
#   scale_fill_brewer(palette = 'Dark2')
# 
# k_d %>%
#   mutate(on_spironolactone = as.factor(on_spironolactone)) %>%
#   ggplot(aes(x = on_spironolactone, y = delta_val)) +
#   geom_boxplot(aes(fill = on_spironolactone)) +
#   scale_fill_brewer(palette = 'Dark2')
# 
# k_d %>%
#   mutate(on_thiazide = as.factor(on_thiazide)) %>%
#   ggplot(aes(x = on_thiazide, y = delta_val)) +
#   geom_boxplot(aes(fill = on_thiazide)) +
#   scale_fill_brewer(palette = 'Dark2')
```


Time reference?
Do we have other ICU data? (without repletion) 'lack of order'
within 24 hours?
based on lab order time stamp
by ORDERS (nursing time stamp)

lasik: 6 hours
bumex: 24 hours
pharmacokinetics

how many dosages (cumulative dose of the medication)


lack of K repletion yields higher risk of mortality after a period of time (few days)?
