---
title: "Reading Files"
output: html_document
---
Setup:

```{r}
library(tidyverse)
library(vroom)
library(lubridate)
```

Testing:

```{r}
data_path <- '../wharton/processed_data/'
ori_data_path <- '../wharton/data/'
# visit_hospital_d <- paste0(data_path, 'visit_hospital.csv') %>% read_csv()
# unique(visit_hospital_d$hospital)

read_d <- function(lyte) paste0(data_path, lyte, '_d.csv') %>% data.table::fread()
read_ori <- function(var){
  dat <- paste0(ori_data_path, var, '.csv') %>%
    data.table::fread(colClasses = c(visit_num = 'integer64')) %>%
    distinct()
  
  # fix issues with duplicates in the daily_labs tables
  if (grepl('_daily_labs', var)){
    lyte <- gsub('_daily_labs', '', var)
    cols <- paste(c('min', 'max'), lyte, 'val', sep = '_')
    dat <- dat %>%
      group_by(visit_num, day_in_unit) %>%
      summarise(!!(cols[1]) := min(!!(sym(cols[1]))),
                !!(cols[2]) := max(!!(sym(cols[2]))))
  }
  
  if ('day_in_unit' %in% colnames(dat)){
    dat <- dat %>%
      mutate(day_in_unit = 
               gsub(' 00:00:00', '', day_in_unit))
  }
  
  dat
}

d <- read_d('k')
mg_d <- read_d('mg')
ca_d <- read_d('ca')
phos_d <- read_d('phos')

colnames(k_d)
table(k_d$medication_name)
table(k_d$hospital)
table(k_d$provider_name)
colnames(k_d)
unique(k_d$medication_name)
```

Calculate GFR by MDRD calculation
female_coeff = 0.742 if is_female==1 else 1
aa_coeff = 1.212 if_aa==1 else 1
(assuming no African-American patients - data not available)
GFR = 175 * Cr^-1.154 * age^-0.203 * female_fac

```{r}
daily_dat <- c('daily_vitals', 'given_fluid_bolus', 'given_beta_blocker', 'given_diltiazem', 'given_amiodarone', 'creatinine', 'is_ventilated', 'potassium_daily_labs', 'magnesium_daily_labs', 'calcium_daily_labs', 'phosphate_daily_labs')

system.time(
 vitals_d <- lapply(daily_dat, read_ori) %>%
  reduce(left_join, by = c('visit_num', 'day_in_unit')) %>%
  list() %>%
  c(lapply(c('age_gender', 'weights', 'visit_hospital'), read_ori)) %>%
  reduce(left_join, by = 'visit_num') %>%
  mutate(gfr_mdrd = 175 *
           creatinine^(-1.154) *
           age^(-0.203) *
           ifelse(is_female, 0.742, 1)) 
)


gfr_info <- vitals_d %>%
  filter(gfr_mdrd > 0 & gfr_mdrd < 30) %>%
  select(visit_num) %>%
  mutate(gfr_mdrd_below_30 = 1)


```


```{r}
k_d_all <- read_ori('potassium_data')
hospital_d <- read_ori('visit_hospital')

```

```{r}
visits <- function(codename){# dat_name and col_name
  paste0(ori_data_path, codename[[1]], '.csv') %>%
    data.table::fread(colClasses = c('integer64')) %>%
    mutate(!!(codename[[2]]) := 1) 
}
code_names <- c(
  'aki-codes', 'is_aki',
  'ckd-codes', 'is_ckd',
  'esrd-codes', 'is_esrd',
  'dialysis-codes', 'is_dialysis',
  'dialysis-proc-patients', 'given_dialysis',
  'paralyzed-codes', 'is_paralyzed',
  'rhabdo-codes', 'is_rhabdo',
  'chf-codes', 'is_chf',
  'cad-codes', 'is_cad',
  'parathyroid-codes', 'is_parathyroid',
  'sarcoid-codes', 'is_sarcoid',
  'afib-codes', 'is_afib',
  'tpn-patients', 'on_tpn',
  'loop-diuretics', 'on_loop_diuretic',
  'thiazides', 'on_thiazide',
  'acetazolamide', 'on_acetazolamide',
  'spironolactone', 'on_spironolactone') %>%
  matrix(nrow = 2) %>%
  t() 

code_list <- code_names %>%
  as_tibble() %>%
  split(.$V1) %>%
  map(visits)


k_ext <- k_d_all %>%
  mutate(delta_val = post_repletion_val - pre_repletion_val) %>%
  group_by(visit_num, 
           pre_repletion_val_date_offset_seconds,
           post_repletion_val_date_offset_seconds) %>%
  add_tally() %>%
  mutate(is_ivpo = as.integer(skimr::n_unique(is_iv) > 1)) %>%
  # Adjust for 4.4 mEq K / 3 mmol P in KH2PO4.
  # Only K dataframe!
  mutate(performed_dose = performed_dose * ifelse(
    (is_iv == 1) & grepl('phosphate', medication_name, ignore.case = T),
    4.4/3.0,
    1)
  ) %>%
  list() %>% 
  c(code_list, list(gfr_info, hospital_d)) %>%
  reduce(left_join, by = 'visit_num') %>%
  mutate_at(code_names[,2], x = replace_na(x, 0)) #%>% # fill in 0 for NAs
  # mutate(performed_day_of_week = performed_date %>% ymd() %>% weekdays())

setdiff(colnames(k_d), colnames(k_ext))
identical(k_d$gfr_mdrd_below_30_x, k_d$gfr_mdrd_below_30_y)
```

Now let's filter:

```{r}
k_fillna <- k_ext %>%
  mutate_at(code_names[, 2], funs(if_else(is.na(.), 0, .) ))

table(k_ext$is_parathyroid)
# Include patients:
k_filtered <- k_ext %>%
  filter(# age >= 18 & # over 18 years old
           # prbc_given == 0 & # no PRBC
           on_tpn == 0 & # not on TPN
           is_rhabdo == 0 & # no rhabdomyolysis code
           is_parathyroid == 0 & # no parathyroid disorders of any kind
           is_sarcoid == 0 & # no sarcoid disorders of any kind
           is_esrd == 0 & # no code for ESRD
           is_dialysis == 0 & # no code for dialysis
           given_dialysis == 0 &# no dialysis procedure
           ! gfr_mdrd_below_30
  )
```




filter(age >= 18) %>% # over 18 years old
Set thresholds:
```{r}
rep_count_threshold <- 20
```




Reproduce some plots:


### At what point do providers replete electrolytes?
Cell 15:

```{r}
k_d %>% group_by(provider_name) %>%
  add_tally(pre_repletion_val) %>%
  filter(n > rep_count_threshold) %>%
  summarise(mean_pre_rep_val = mean(pre_repletion_val)) %>%
  ggplot(aes(x = mean_pre_rep_val)) +
  geom_histogram(binwidth = 0.1) +
  labs(y = 'Number of providers')


# mydat <- k_d %>% group_by(provider_name) %>%
#   summarise(mean_pre_rep_val = mean(pre_repletion_val))
# hist(mydat$mean_pre_rep_val)
# ggplot(mydat, aes(x = mean_pre_rep_val)) +
#   geom_histogram(binwidth = 0.5)
```

Cell 17:

```{r}
boxplot(k_d$result_to_order_seconds)
ymd_hms(k_d$performed_date) - ymd(k_d$result_to_order_seconds)
```


```{r}
ymd_hms(k_d$performed_date) %>% hour()
```


Cell 21:

```{r}
days <- c('Mon', 'Tue', 'Wed', 'Thu', 'Fri', 'Sat', 'Sun')
k_d %>%
  group_by(performed_day_of_week) %>%
  summarise(mean_pre_val = mean(pre_repletion_val)) %>%
  ggplot(aes(x = performed_day_of_week,
             y = mean_pre_val)) +
  geom_point() +
  scale_y_continuous(limits = c(0, 3.7))
```


### What are the pre- and post-repletion electrolyte lab values?
```{r}
k_d %>%
  dplyr::select(pre_repletion_val, post_repletion_val) %>%
  gather('prepost', 'value') %>%
  ggplot(aes(x = value, fill = prepost)) +
  geom_histogram(alpha = 0.7, position = 'identity', binwidth = 0.1)
```


```{r}
delta_repletion <- k_d %>%
  transmute(delta_repletion = post_repletion_val - pre_repletion_val) %>%
  pull()

# delta_repletion <- mg_d %>%
#   transmute(delta_repletion = post_repletion_val - pre_repletion_val) %>%
#   pull()
sum(delta_repletion < 0)/length(delta_repletion) # 23%
ineffective_proportion(mg_d) # 20%
sum(phos_d$delta_val < 0)/length(phos_d$delta_val) # 16%
sum(ca_d$delta_val < 0)/length(ca_d$delta_val) # 20%

ineffective_proportion <- function(elec){
  sum(elec$delta_val < 0)/length(elec$delta_val) # 20%
}


cor.test(delta_repletion, k_d$on_acetazolamide)
# t.test(alternative = 'greater')

# last 6 hours dialysis, +/- 12 hours
# excluded dialysis
# why?
# same patient: K drop, K increase?
# heart rate: heart beat high
# drug datasets


```








```{r}
lm(order_to_repletion_seconds ~ pre_repletion_val + is_cad + is_chf + is_ckd + on_loop_diuretic + on_acetazolamide + on_thiazide + on_spironolactone, data = k_d) %>%
  summary() %>%
  broom::tidy()
```

```{r}
lm(delta_val ~ performed_dose + 
     pre_repletion_val +
     is_cad + is_chf + is_ckd + on_loop_diuretic + on_acetazolamide + on_thiazide + on_spironolactone, data = k_d) %>%
  summary() %>%
  broom::tidy() %>%
  mutate(padj = p.adjust(p.value, method = 'BH'))

lm(delta_val ~ performed_dose + is_cad + is_chf + is_ckd + on_loop_diuretic + on_acetazolamide + on_thiazide + on_spironolactone, data = k_d) %>%
  summary() %>%
  broom::tidy()

cor(k_d$performed_dose, k_d$delta_val)

```

```{r}
# extend k_d dataset
k_d_ext <- k_d %>%
  transmute(t_order = order_date_offset_seconds - pre_repletion_val_date_offset_seconds,
         t_RN = performed_date_offset_seconds - pre_repletion_val_date_offset_seconds,
         t_orderlab = post_repletion_val_order_date_offset_seconds - pre_repletion_val_date_offset_seconds,
         t_resultlab = post_repletion_val_date_offset_seconds - post_repletion_val_order_date_offset_seconds,
         t_repletion_orderlab_overlap = post_repletion_val_order_date_offset_seconds - performed_date_offset_seconds,
         t_repletion_resultlab_overlap = post_repletion_val_date_offset_seconds - performed_date_offset_seconds,
         weekend = performed_day_of_week >= 5)

ggplot(aes(x = t_order/60, fill = weekend), data = k_d_ext) +
  geom_histogram(bins = 300, stat = 'density',
                 position = 'identity', alpha = 0.8) +
  scale_x_continuous(limits = c(-20000/60, 86400/60))
  labs(x = 'Time since initial lab resulted, in minutes',
       y = 'Proportion of occurrences')
```


Focus on depletion of > 4.5

```{r}
k_d %>%
  filter(pre_repletion_val > 4.5) %>%
  nrow()
#2303

k_d %>%
  filter(pre_repletion_val > 4.5) %>%
  count(provider_name) %>%
  # filter(n >= 10) %>%
  nrow()
# Providers that perform improper repletion: 669

k_d %>%
  filter(pre_repletion_val > 4.5) %>%
  count(provider_name) %>%
  filter(n >= 10) %>%
  nrow()

# Are these providers over prescribe for Mg? Yes.
mg_d %>%
  filter(pre_repletion_val > 2.5) %>%
  nrow()
#2303

mg_d %>%
  filter(pre_repletion_val > 2.5) %>%
  count(provider_name) %>%
  # filter(n >= 10) %>%
  nrow()
# Providers that perform improper repletion: 669

mg_d %>%
  filter(pre_repletion_val > 2.5) %>%
  count(provider_name) %>%
  filter(n >= 10) %>%
  nrow()


# function in the system?
# overprotective? defensive? systematic error?
# why K drop?




k_d %>%
  filter(pre_repletion_val > 4.5) %>%
  dplyr::select(provider_name, hospital) %>%
  count(hospital)

k_d %>%
  # filter(pre_repletion_val > 4.5) %>%
  dplyr::select(provider_name, hospital) %>%
  count(hospital)


# some providers change hospitals

  # filter(n >= 10) %>%


k_d %>%
  count(provider_name) %>%
  nrow()
# Total number of providers: 2040

669/2040
```



```{r}
dat_high_pre <- k_d_ext %>%
  filter(pre_repletion_val > 4.5)

dat_high_pre %>%
  nrow()
#2303



ggplot(aes(x = t_order/60, fill = weekend), data = dat_high_pre) +
  geom_histogram(bins = 300, stat = 'density',
                 position = 'identity', alpha = 0.8) +
  scale_x_continuous(limits = c(-20000/60, 86400/60))
  labs(x = 'Time since initial lab resulted, in minutes',
       y = 'Proportion of occurrences')

# of the 2303 improper repletions, how many are before lab results come
dat_high_pre %>%
  filter(t_order < 0) %>%
  filter(t_order > -20000) %>%
  nrow()
#181

k_d_ext %>%
  filter(t_order < 0) %>%
  filter(t_order > -20000) %>%
  nrow()
#5947
```


Drugs to consider:
- Furosemide
- Lasix
- Spironolactone
- Diamox
- HCTZ
- Hydrochlorothiazide
- bumex

```{r}
# meds_d <- data.table::fread('../../Penn_ICU_Data/ICU PTS COHORT MEDS.csv')
# save(meds_d, file = '../wharton/data/medications.Rdata')

# load('../wharton/data/medications.Rdata')
colnames(meds_d)
head(meds_d)
table(meds_d$MEDICATION_NAME[1:1000])
```

```{r}
# slice_drugs <- function(drug_name){
#   meds_d %>%
#     filter(grepl(drug_name, MEDICATION_NAME, ignore.case = T))
# }
# diamox <- slice_drugs("diamox|acetazolamide")
# bumex <- slice_drugs("bumex|bumetanide")
# hctz <- slice_drugs("microzide|hydrochlorothiazide|HCTZ")
# spironolactone <- slice_drugs("spironolactone|caroSpir|aldactone")
# lasix <- slice_drugs("lasix|furosemide")
# save(diamox, bumex, hctz, spironolactone, lasix,
#      file = '../wharton/data/blood_pressure_meds.Rdata')
# 
load('../wharton/data/blood_pressure_meds.Rdata')
```

```{r}
head(diamox)
diamox <- diamox %>%
  mutate(diamox_date = mdy_hms(
    PERFORMED_DATE, 
    format = '%m/%d/%Y %H.%M.%S %p')
    [-(nrow(diamox) +1)])
head(k_d)
```


```{r}
k_d_time <- k_d %>%
  mutate(k_date = ymd_hms(
    performed_date, 
    format = '%Y-%m-%d %H:%M:%S')
    [-(nrow(k_d) +1)])


head(ymd_hms(k_d$performed_date, 
    format = '%Y-%m-%d %H:%M:%S'))

colnames(k_d)
# k_d$post_hr_max


head(k_d$performed_date)
head(diamox$PERFORMED_DATE)
head(as.Date(diamox$PERFORMED_DATE, format = '%m/%d/%Y %H.%M.%S %p'))
library(lubridate)
date_test <- mdy_hms(diamox$PERFORMED_DATE, format = '%m/%d/%Y %H.%M.%S %p')
length(diamox$PERFORMED_DATE)
length(date_test)
tail(date_test)
tail(diamox$PERFORMED_DATE, 5)
diamox$PERFORMED_DATE[which(is.na(date_test))]
dhours(date_test[1] - date_test[2])

date_test[1] %within% 
  interval(date_test[1] - hours(12), date_test[1] + hours(12))
```



```{r}
k_d %>%
  mutate(on_acetazolamide = as.factor(on_acetazolamide)) %>%
  ggplot(aes(x = on_acetazolamide, y = delta_val)) +
  geom_boxplot(aes(fill = on_acetazolamide)) +
  scale_fill_brewer(palette = 'Dark2')

k_d %>%
  mutate(on_spironolactone = as.factor(on_spironolactone)) %>%
  ggplot(aes(x = on_spironolactone, y = delta_val)) +
  geom_boxplot(aes(fill = on_spironolactone)) +
  scale_fill_brewer(palette = 'Dark2')

k_d %>%
  mutate(on_thiazide = as.factor(on_thiazide)) %>%
  ggplot(aes(x = on_thiazide, y = delta_val)) +
  geom_boxplot(aes(fill = on_thiazide)) +
  scale_fill_brewer(palette = 'Dark2')
```


Time reference?
Do we have other ICU data? (without repletion) 'lack of order'
within 24 hours?
based on lab order time stamp
by ORDERS (nursing time stamp)

lasik: 6 hours
bumex: 24 hours
pharmacokinetics

how many dosages (cumulative dose of the medication)


lack of K repletion yields higher risk of mortality after a period of time (few days)?
